Latent Group Dropout for Multilingual and Multidomain Machine Translation

### 2022-05-16 2022/acl/acl_latex.tex
local changes

\author{
  MinhQuang Pham$^{\dag\ddag}$, \ \ Josep Crego$^\dag$,\ \ Fran\c cois Yvon$^\ddag$ \\
  $^\dag$SYSTRAN / 5 rue Feydeau, 75002 Paris, France\\
  {\tt firstname.lastname@systrangroup.com}\\
  $^\ddag$Universit\'e Paris-Saclay, CNRS, LISN,  91405 Orsay, France\\
  {\tt firstname.lastname@limsi.fr}
}

@@

Because:
\begin{align*}
\hspace{-3.em}
\lim_{\tau \rightarrow 0} \sigma(\frac{g_l^d(i) + \Phi_l^d(i) + \nu}{\tau}) = \begin{cases}
      1, & \text{if}\ \tau > - (g_l^d(i) + \Phi_l^d(i)), \\
      0, & \text{if}\ \tau < - (g_l^d(i) + \Phi_l^d(i)), \\
      \frac{1}{2} &\text{otherwise}\\
    \end{cases}
\end{align*}

>>>>

\author{MinhQuang Pham$^{\dag\ddag}$\thanks{$\ \ \ \ $Now Research Scientist at Zoom Video Communications}, \ \ Josep Crego$^\dag$,\ \ Fran\c cois Yvon$^\ddag$ \\
  $^\dag$SYSTRAN / 5 rue Feydeau, 75002 Paris, France\\
  {\tt firstname.lastname@systrangroup.com}\\
  $^\ddag$Universit\'e Paris-Saclay, CNRS, LIMSI,  91405 Orsay, France\\
  {\tt firstname.lastname@limsi.fr}}

@@

Because:
\begin{align*}
\lim_{\tau \rightarrow 0} \sigma(\frac{g_l^d(i) + \Phi_l^d(i) + \nu}{\tau}) = \\
= \begin{cases}
      1, & \text{if}\ \tau > - (g_l^d(i) + \Phi_l^d(i)), \\
      0, & \text{if}\ \tau < - (g_l^d(i) + \Phi_l^d(i)), \\
      \frac{1}{2} &\text{otherwise}\\
    \end{cases}
\end{align*}
